Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps

### 2018-11-21 IPCO format/introduction.tex
little fix
lemma2 proof

Known polyhedral structure makes it easier to study integrality gaps for such problems. 
\cindy{Is this right?  That citation is for Carr and Vempala.}
Carr and Ravi \cite{carr-ravi} introduced the notion of fundamental extreme points. A point x in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.  We say a fundamental extreme point (FEP) is {\em order $k$} if there are $k$ nodes on this Hamiltonian cycle. An FEP of order $k$ could represent an instance with many more than $k$ vertices. Carr and co-authors~\cite{CV,carr-ravi,Boyd-Carr-2011} proved that showing that $Cx$ is a convex combination of tours (resp. 2-edge-connected subgraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp. 2EC) is bounded above by $C$. Thus we can create the ``hardest'' LP solutions to decompose.

There are fairly good bounds known for the integrality gap for TSP or $\EC$. \cindy{Arash, please confirm this change is correct.}Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Also,  Alexander et. al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on graphs with at most 10 vertices. For $\EC$ we can show that the integrality gap of $\EC$ is at most $\frac{6}{5}$ for FEPs of order at most 12.
%In fact, since FDT can be applied to different problem, we can use it to evaluate the integrality gap of other well-known problem.
For TAP, we create random fractional extreme points and round them using FDT. For the instances that we create the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.

>>>>

Known polyhedral structure makes it easier to study integrality gaps for such problems. 
\cindy{Is this right?  That citation is for Carr and Vempala.}
Carr and Ravi \cite{carr-ravi} introduced the notion of fundamental extreme points. A point x in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.  We say a fundamental extreme point (FEP) is {\em order $k$} if there are $k$ nodes on this Hamiltonian cycle. An FEP of order $k$ could represent an instance with many more than $k$ vertices. Carr and co-authors~\cite{CV,carr-ravi, Boyd-Carr-2011} proved that showing that $Cx$ is a convex combination of tours (resp. 2-edge-connected subgraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp. 2EC) is bounded above by $C$. Thus we can create the ``hardest'' LP solutions to decompose.

There are fairly good bounds known for the integrality gap for TSP or $\EC$. \cindy{Arash, please confirm this change is correct.}Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Also,  Alexander et. al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on graphs with at most 10 vertices. For $\EC$ we can show that the integrality gap of $\EC$ is at most $\frac{6}{5}$ for FEPs of order at most 12. Notice an FEP of order $k$ might correspond to an extreme point of a much bigger graph, since each edge in a FEP with value 1, actually corresponds to a path of edges with value 1.
%In fact, since FDT can be applied to different problem, we can use it to evaluate the integrality gap of other well-known problem.
For TAP, we create random fractional extreme points and round them using FDT. For the instances that we create the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.
